---
title: "Using R for calculating Premium"
author: "Indira Aryal"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Required Package

This method install package if its not install other wise load. Remember to install pacman package

```{r}
pacman::p_load(dplyr,tidyr,readxl)


```

# Data Reading and Cleaning

Most of the time, Rates of premium are in triangular shape which needs to be converted into column wise tabular data

```{r}
endowment= read_excel("endowment.xlsx")

df<- endowment %>%
  pivot_longer(cols = 2:ncol(endowment),
               names_to = "term",values_to = "rate") 

colnames(df)<-c("age","term","rate")
df <- df %>%
  group_by(age,term) %>%
  distinct(.keep_all = T) %>%
  mutate(term=as.integer(term)) %>%
  ungroup()


```

# Create a function to return rate

For this project, i have created simple function with out considering age limit, term factor in my function.But in case if some one wants, it is possible

```{r}

premium_rate= function(age1,term1){
  
     df %>%
      filter(age == age1 & term == term1 )-> df1

    return(df1$rate)
}

```

# Create dummy data

Now lets see if our function works or not and return rate is correct or not.

```{r}
# example 1
premium_rate(16,9)

#example 2
age1=c(16,19,21,20)
term1=c(9,9,12,17)
SA=c(100000,200000,300000,500000)

df3<- data.frame(age1,term1,SA)
head(df3)

df3 <- df3 %>%
  mutate(rate=premium_rate(age1 = (age1),term1 = (term1)),
         premium=rate*SA/1000)

head(df3)
```
